\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{tikz}
\input{glyphtounicode}
\usepackage[sc]{mathpazo}
\linespread{0.76}
\usepackage[T1]{fontenc}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\cvitem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}
\newcommand{\cvheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}\justifying}
\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}
\newcommand{\cvskill}[2]{
  \textcolor{black}{\textbf{#1}}\hfill
  \foreach \x in {1,...,5}{%
    \space{\ifnumgreater{\x}{#2}{\color{black!80!white!20}}{\color{black}}\faSquare}}\par%
  \vspace{-2pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\footnotesize$\bullet$}}$}
\begin{document}

\begin{center}
  \textbf{\LARGE\scshape AMIR AGASSI} \\
  \vspace{1pt}\small
  \href{https://github.com/amiragassi}{GitHub}
  $\ \diamond\ $
  \href{https://amiragassi.com}{amiragassi.com}
  $\ \diamond\ $ 
  \href{mailto:amiragassi04@gmail.com}{amiragassi04@gmail.com}
  $\ \diamond\ $
  \href{https://www.linkedin.com/in/amir-agassi/}{LinkedIn}
\end{center}

\section{Education}
\cvheadingstart
  \cvheading
    {Wilfrid Laurier University}{\textbf{Waterloo, Ontario}}
    {BSc Computer Science}{2022 - 2026}
  \cvheading
    {Western Governors University}{\textbf{Remote}}
    {Accelerated BSc Cybersecurity \& Information Assurance}{Sept. 2024 - Feb. 2025}
\cvheadingend

\section{Professional Experience}
\cvheadingstart
  \cvheading
    {Shopify}{\textbf{Toronto, Ontario}}
    {Software Engineer Intern - Infrastructure Engineering}{January 2025 - April 2025}
  \cvitemstart
    \cvitem{Assisting the Infrastructure Engineering team in designing scalable cloud solutions, automating deployments, and enhancing monitoring tools to improve platform reliability and performance for millions of global merchants.}
  \cvitemend


  \cvheading
    {Konfer Inc.}{\textbf{Waterloo, Ontario}}
    {Vice President of Engineering}{July 2024 - Present}
  \cvitemstart
    \cvitem{Lead the development of the company's engineering strategy and technical direction, overseeing the organization of 5+ high-impact tech events (networking events, hackathons \& more) annually, connecting innovative businesses with ambitious students and young professionals.}
  \cvitemend

  \cvheading
    {Civiconnect}{\textbf{Remote}}
    {Web Development Associate, Co-op}{September 2024 - Present}
  \cvitemstart
    \cvitem{Collaborated with the Web Development Team to design, develop, and maintain web applications for small to medium-sized businesses, contributing to 3+ client projects using Figma, React, and Supabase.}
  \cvitemend

  \cvheading
    {Sterling Karamar Inc.}{\textbf{Toronto, Ontario}}
    {Junior Software Developer}{July 2021 - August 2022}
  \cvitemstart
    \cvitem{Developed custom large-scale reporting software, facilitating efficient report generation for 85+ corporate real-estate clients, reducing monthly accounting and report creation time by up to 95\% compared to manual creation.}
  \cvitemend

  \cvheading
    {360 Business Marketing Inc.}{\textbf{Concord, Ontario}}
    {Digital Solutions Specialist}{June 2020 - April 2021}
  \cvitemstart
    \cvitem{Engineered and implemented custom analytics dashboard to monitor website traffic and user behavior used with 120+ clients, enabling data-driven decision-making and improving lead generation rates by up to 40\%.}
  \cvitemend

  \cvheading
    {MIT Consulting Inc.}{\textbf{North York, Ontario}}
    {IT Support}{January 2020 - May 2020}
  \cvitemstart
    \cvitem{Developed software in Java \& Python to automate routine tasks \& provided network services to 15+ small businesses.}
  \cvitemend
\cvheadingend

\section{Activities}
\cvheadingstart
  \cvheading
    {Laurier Computing Society}{\textbf{Waterloo, Ontario}}
    {Vice President of Development \& Technology}{January 2024 - Present}
  \cvitemstart
    \cvitem{Overseeing the development and maintenance of society's technical infrastructure, organizing 10+ tech-related events and workshops per semester, with an average attendance of 75 students.}
  \cvitemend

  \cvheading
    {HawkHacks}{\textbf{Waterloo, Ontario}}
    {Software Engineer}{November 2023 - August 2024}
  \cvitemstart
    \cvitem{Contributed to the hackathon's digital infrastructure by developing a full-stack solution for the landing page and hacker dashboard using React and Firebase, supporting 850+ participants \& 1100+ applicants.}
  \cvitemend

  \cvheading
    {Computing Councils of Canada}{\textbf{Remote}}
    {Director of Systems Administration}{November 2022 - Present}
  \cvitemstart
    \cvitem{Led the development of a responsive landing page, Discord bot, 3 software-related projects, and held tech events with the systems administration team, connecting a community of 900+ students in computing clubs across Canada.}
  \cvitemend
\cvheadingend

\section{Projects}
\cvheadingstart
\item
\cvitemstart
  \cvitem{\textbf{\href{https://github.com/KonferCA/SPUR}{SPUR IC OnBoard:}} Developed SPUR Innovation Center's streamlined digital platform to manage startup on-boarding, review, and funding processes for SPUR administrators, startup applicants, and investors. Developed using Go and React, using tools like Docker and PostgreSQL.}

  \vspace{6pt}
  \cvitem{\textbf{\href{https://github.com/AmirAgassi/Danghui-LVM}{Danghui-cLVM:}} Proof of concept Roblox ACE exploit to execute arbitrary code \& fully replicate the scripts to player's machines, affecting 37.1 million daily active players \& aiding in the implementation of their replication filter.}
  \vspace{0pt}
  \vspace{6pt}
  \cvitem{\textbf{\href{https://quickreports.me}{QuickReports:}} A React-based web application in use by 2 medium-sized marketing agencies, helping integrate 8+ digital marketing analytics tools into a single dashboard \& enabling agencies to generate comprehensive reports from consolidated data sources 80\% faster, currently supplying 164+ businesses' monthly reports.}
  \vspace{0pt}
\cvitemend
\cvheadingend

\section{Certifications}
\cvheadingstart
\item
\cvitemstart
  \cvitem{
    {\href{https://cp.certmetrics.com/amazon/en/public/verify/credential/2LC36B3CWM411J3K}{AWS Certified Solutions Architect - Professional}} •
    {ITIL 4 Foundation - IT Service Management}
  }
  \cvitem{
    {\href{https://www.certmetrics.com/comptia/public/verification.aspx/}{CompTIA A+ IT}} •
    {\href{https://www.certmetrics.com/comptia/public/verification.aspx/}{CompTIA Network+}} •
    {CompTIA IT Operations Specialist} •
    {CompTIA Secure Infra Specialist}
  }
\cvitemend
\cvheadingend

\end{document}
